A fast and memory-efficient transition state search method for complex energy landscapes

### 2022-04-21 manuscript.tex
Figures font and dpi updated
Changed bib to nature style

\section{Results and discussion}
\subsection{BITSS method}
\begin{figure}[htb]
  \includegraphics{toy2d.pdf}
  \caption{\label{fig:toy2d}
    (a) The trajectories of the two states under the BITSS method (orange line) for a simple 2D potential with two minima (blue dots).
        The transition state is shown by a red dot, and the minimum energy pathway by the dashed line.
    (b) A snapshot of the BITSS minimisation showing the driving forces on each state due to the energy constraint, $\bm{F}_E$, and distance constraint, $\bm{F}_D$, with $E_1 < E_2$ and $\mathrm{d}(\bm{x}_1,\bm{x}_2) < d_i$.
    (c) The final configuration of the BITSS method showing the two states in orange, the transition state in red, and the negative curvature eigenvector, $\bm{\hat{\tau}}$.
  }
\end{figure}

@@

\subsection{Speed Comparison}
\begin{figure*}[tb]
  \includegraphics{speedtest.pdf}
  \caption{\label{fig:speedtest}
    Comparisons between BITSS, DNEB, and the string method in the convergence to the transition state as a function of the number of calculations of the energy gradient.
    Three test systems are used: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
    The configurations shown correspond to the two minimum energy states and the transition state, marked by an asterisk.
    The string method and DNEB are repeated with a differing number of images, as listed in the legend in (c).
  }
\end{figure*}

@@

\subsection{Adaptive discretisation}
\label{sec:adaptive}
\begin{figure}[tb]
  \includegraphics{adaptivemesh.pdf}
  \caption{\label{fig:adaptivemesh}
    (a) Snapshots of the BITSS method applied to the buckling of a cylinder with a changing mesh.
        The radial displacement relative the unbuckled cylinder is shown, as well as the underlying triangular mesh.
    (b) BITSS applied to the striped wetting example with different resolutions for the two states.
        Each grid cell denotes 50x50 lattice nodes.
        The zoomed axis shows the difference in the fluid interface between the two final states, as well as the approximated transition state (solid black line).
        This is compared to the transition state found using a high resolution (dashed line).
  }
\end{figure}

@@

\subsection{Complex landscapes}
\begin{figure}[tb]
  \includegraphics{flatdiscontinuous.pdf}
  \caption{\label{fig:flatdiscontinuous}
    (a) Energy profile of the BITSS pathway on a 2D potential with flat regions.
        Blue and red dots denote the minima and transition state, respectively.
        Points of interest are labelled by i--iii (see text).
        Top inset: A zoomed in view around the transition state.
        Bottom inset: The pathway taken, with the edges of the flat regions marked by dashed lines.
    (b) Disconnectivity graph of the energy landscape for a seven-particle cluster with a discontinuous hard-core pair potential (orange), and a standard Lennard-Jones potnetial (gray).
        The two graphs are offset for visibility.
    (c) Plot of the discontinuous potential.
        The repulsive section of the standard Lennard-Jones potential is also shown in grey.
  }
\end{figure}

@@

%% start bib
% \bibliography{bibexport.bib}
% % \bibliography{../../library.bib}
% % \bibliographystyle{apsrev4}
%% mid bib
\begin{thebibliography}{51}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
\expandafter\ifx\csname bibnamefont\endcsname\relax
  \def\bibnamefont#1{#1}\fi
\expandafter\ifx\csname bibfnamefont\endcsname\relax
  \def\bibfnamefont#1{#1}\fi
\expandafter\ifx\csname citenamefont\endcsname\relax
  \def\citenamefont#1{#1}\fi
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem[{\citenamefont{Bryngelson et~al.}(1995)\citenamefont{Bryngelson,
  Onuchic, Socci, and Wolynes}}]{Bryngelson1995}
\bibinfo{author}{\bibfnamefont{J.~D.} \bibnamefont{Bryngelson}},
  \bibinfo{author}{\bibfnamefont{J.~N.} \bibnamefont{Onuchic}},
  \bibinfo{author}{\bibfnamefont{N.~D.} \bibnamefont{Socci}}, \bibnamefont{and}
  \bibinfo{author}{\bibfnamefont{P.~G.} \bibnamefont{Wolynes}},
  \bibinfo{journal}{Proteins: Structure, Function, and Bioinformatics}
  \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{167} (\bibinfo{year}{1995}).

\bibitem[{\citenamefont{Onuchic et~al.}(1997)\citenamefont{Onuchic,
  Luthey-Schulten, and Wolynes}}]{Onuchic1997}
\bibinfo{author}{\bibfnamefont{J.~N.} \bibnamefont{Onuchic}},
  \bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Luthey-Schulten}},
  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{P.~G.}
  \bibnamefont{Wolynes}}, \bibinfo{journal}{Annual Review of Physical
  Chemistry} \textbf{\bibinfo{volume}{48}}, \bibinfo{pages}{545}
  (\bibinfo{year}{1997}).

\bibitem[{\citenamefont{Boehr et~al.}(2006)\citenamefont{Boehr, McElheny,
  Dyson, and Wrightt}}]{Boehr2006}
\bibinfo{author}{\bibfnamefont{D.~D.} \bibnamefont{Boehr}},
  \bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{McElheny}},
  \bibinfo{author}{\bibfnamefont{H.~J.} \bibnamefont{Dyson}}, \bibnamefont{and}
  \bibinfo{author}{\bibfnamefont{P.~E.} \bibnamefont{Wrightt}},
  \bibinfo{journal}{Science} \textbf{\bibinfo{volume}{313}},
  \bibinfo{pages}{1638} (\bibinfo{year}{2006}).

\bibitem[{\citenamefont{Kerns et~al.}(2015)\citenamefont{Kerns, Agafonov, Cho,
  Pontiggia, Otten, Pachov, Kutter, Phung, Murphy, Thai et~al.}}]{Kerns2015}
\bibinfo{author}{\bibfnamefont{S.~J.} \bibnamefont{Kerns}},
  \bibinfo{author}{\bibfnamefont{R.~V.} \bibnamefont{Agafonov}},
  \bibinfo{author}{\bibfnamefont{Y.~J.} \bibnamefont{Cho}},
  \bibinfo{author}{\bibfnamefont{F.}~\bibnamefont{Pontiggia}},
  \bibinfo{author}{\bibfnamefont{R.}~\bibnamefont{Otten}},
  \bibinfo{author}{\bibfnamefont{D.~V.} \bibnamefont{Pachov}},
  \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Kutter}},
  \bibinfo{author}{\bibfnamefont{L.~A.} \bibnamefont{Phung}},
  \bibinfo{author}{\bibfnamefont{P.~N.} \bibnamefont{Murphy}},
  \bibinfo{author}{\bibfnamefont{V.}~\bibnamefont{Thai}}, \bibnamefont{et~al.},
  \bibinfo{journal}{Nature Structural and Molecular Biology}
  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{124} (\bibinfo{year}{2015}).

\bibitem[{\citenamefont{Guo et~al.}(2018)\citenamefont{Guo, Wang, Wang, Wang,
  and Hu}}]{Guo2018a}
\bibinfo{author}{\bibfnamefont{C.}~\bibnamefont{Guo}},
  \bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Wang}},
  \bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Wang}},
  \bibinfo{author}{\bibfnamefont{H.~F.} \bibnamefont{Wang}}, \bibnamefont{and}
  \bibinfo{author}{\bibfnamefont{P.}~\bibnamefont{Hu}},
  \bibinfo{journal}{Journal of Physical Chemistry C}
  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{21478}
  (\bibinfo{year}{2018}).

\bibitem[{\citenamefont{Richardson et~al.}(2016)\citenamefont{Richardson,
  P{\'{e}}rez, Lobsiger, Reid, Temelso, Shields, Kisiel, Wales, Pate, and
  Althorpe}}]{Richardson2016}
\bibinfo{author}{\bibfnamefont{J.~O.} \bibnamefont{Richardson}},
  \bibinfo{author}{\bibfnamefont{C.}~\bibnamefont{P{\'{e}}rez}},
  \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Lobsiger}},
  \bibinfo{author}{\bibfnamefont{A.~A.} \bibnamefont{Reid}},
  \bibinfo{author}{\bibfnamefont{B.}~\bibnamefont{Temelso}},
  \bibinfo{author}{\bibfnamefont{G.~C.} \bibnamefont{Shields}},
  \bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Kisiel}},
  \bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
  \bibinfo{author}{\bibfnamefont{B.~H.} \bibnamefont{Pate}}, \bibnamefont{and}
  \bibinfo{author}{\bibfnamefont{S.~C.} \bibnamefont{Althorpe}},
  \bibinfo{journal}{Science} \textbf{\bibinfo{volume}{351}},
  \bibinfo{pages}{1310} (\bibinfo{year}{2016}).

\bibitem[{\citenamefont{Vaillant et~al.}(2019)\citenamefont{Vaillant, Althorpe,
  and Wales}}]{Vaillant2019}
\bibinfo{author}{\bibfnamefont{C.~L.} \bibnamefont{Vaillant}},
  \bibinfo{author}{\bibfnamefont{S.~C.} \bibnamefont{Althorpe}},
  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
  \bibinfo{journal}{Journal of Chemical Theory and Computation}
  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{33} (\bibinfo{year}{2019}).

\bibitem[{\citenamefont{Richard and Speck}(2018)}]{Richard2018}
\bibinfo{author}{\bibfnamefont{D.}~\bibnamefont{Richard}} \bibnamefont{and}
  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Speck}},
  \bibinfo{journal}{The Journal of Chemical Physics}
  \textbf{\bibinfo{volume}{148}}, \bibinfo{pages}{124110}
  (\bibinfo{year}{2018}).

\bibitem[{\citenamefont{Wales et~al.}(1998)\citenamefont{Wales, Miller, and
  Walsh}}]{Wales1998}
\bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
  \bibinfo{author}{\bibfnamefont{M.~A.} \bibnamefont{Miller}},
  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{T.~R.} \bibnamefont{Walsh}},
  \bibinfo{journal}{Nature} \textbf{\bibinfo{volume}{394}},
  \bibinfo{pages}{758} (\bibinfo{year}{1998}).

\bibitem[{\citenamefont{Wales}(2012)}]{Wales2012}
\bibinfo{author}{\bibfnamefont{D.~J.} \bibnamefont{Wales}},
  \bibinfo{journal}{Philosophical Transactions of the Royal Society A:
  Mathematical, Physical and Engineering Sciences}
  \textbf{\bibinfo{volume}{370}}, \bibinfo{pages}{2877} (\bibinfo{year}{2012}).

\bibitem[{\citenamefont{Panter et~al.}(2019{\natexlab{a}})\citenamefont{Panter,
  Chen, Zhang, and Kusumaatmaja}}]{Panter2019}
\bibinfo{author}{\bibfnamefont{J.~R.} \bibnamefont{Panter}},
  \bibinfo{author}{\bibfnamefont{J.}~\bibnamefont{Chen}},
  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Zhang}}, \bibnamefont{and}
  \bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{Kusumaatmaja}},
  \bibinfo{journal}{Communications Physics} \textbf{\bibinfo{volume}{2}},
  \bibinfo{pages}{151} (\bibinfo{year}{2019}{\natexlab{a}}).

\bibitem[{\citenamefont{Hutchinson and Thompson}(2018)}]{Hutchinson2018}
\bibinfo{author}{\bibfnamefont{J.~W.} \bibnamefont{Hutchinson}}
  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{J.~M.~T.}
  \bibnamefont{Thompson}}, \bibinfo{journal}{International Journal of Solids
  and Structures} \textbf{\bibinfo{volume}{148-149}}, \bibinfo{pages}{157}
  (\bibinfo{year}{2018}).

\bibitem[{\citenamefont{Zhang and Ren}(2014)}]{Zhang2014}
\bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Zhang}} \bibnamefont{and}
  \bibinfo{author}{\bibfnamefont{W.}~\bibnamefont{Ren}}, \bibinfo{journal}{The
  Journal of Chemical Physics} \textbf{\bibinfo{volume}{141}},
  \bibinfo{pages}{244705} (\bibinfo{year}{2014}).

\bibitem[{\citenamefont{Panter et~al.}(2019{\natexlab{b}})\citenamefont{Panter,
  Gizaw, and Kusumaatmaja}}]{Panter2019b}
\bibinfo{author}{\bibfnamefont{J.~R.} \bibnamefont{Panter}},
  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Gizaw}}, \bibnamefont{and}
  \bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{Kusumaatmaja}},
  \bibinfo{journal}{Science Advances} \textbf{\bibinfo{volume}{5}},
  \bibinfo{pages}{eaav7328} (\bibinfo{year}{2019}{\natexlab{b}}).

\bibitem[{\citenamefont{Amabili et~al.}(2017)\citenamefont{Amabili, Giacomello,
  Meloni, and Casciola}}]{Amabili2017}
\bibinfo{author}{\bibfnamefont{M.}~\bibnamefont{Amabili}},
  \bibinfo{author}{\bibfnamefont{A.}~\bibnamefont{Giacomello}},
  \bibinfo{author}{\bibfnamefont{S.}~\bibnamefont{Meloni}}, \bibnamefont{and}
  \bibinfo{author}{\bibfnamefont{C.~M.} \bibnamefont{Casciola}},
  \bibinfo{journal}{Physical Review Fluids} \textbf{\bibinfo{volume}{2}},
  \bibinfo{pages}{034202} (\bibinfo{year}{2017}).

\bibitem[{\citenamefont{Othayoth et~al.}(2020)\citenamefont{Othayoth, Thoms,
  and Li}}]{Othayoth2020}
\bibinfo{author}{\bibfnamefont{R.}~\bibnamefont{Othayoth}},
  \bibinfo{author}{\bibfnamefont{G.}~\bibnamefont{Thoms}}, \bibnamefont{and}
  \bibinfo{author}{\bibfnamefont{C.}~\bibnamefont{Li}},
  \bibinfo{journal}{Proceedings of the National Academy of Sciences}
  \textbf{\bibinfo{volume}{117}}, \bibinfo{pages}{14987}
  (\bibinfo{year}{2020}).

\bibitem[{\citenamefont{Filipov et~al.}(2015)\citenamefont{Filipov, Tachi,
  Paulino, and Weitz}}]{Filipov2015}
\bibinfo{author}{\bibfnamefont{E.~T.} \bibnamefont{Filipov}},
  \bibinfo{author}{\bibfnamefont{T.}~\bibnamefont{Tachi}},
  \bibinfo{author}{\bibfnamefont{G.~H.} \bibnamefont{Paulino}},
  \bibnamefont{and} \bibinfo{author}{\bibfnamefont{D.~A.} \bibnamefont{Weitz}},
  \bibinfo{journal}{Proceedings of the National Academy of Sciences of the
  United States of America} \textbf{\bibinfo{volume}{112}},
  \bibinfo{pages}{12321} (\bibinfo{year}{2015}).

\bibitem[{\citenamefont{Zhai et~al.}(2018)\citenamefont{Zhai, Wang, and
  Jiang}}]{Zhai2018}
\bibinfo{author}{\bibfnamefont{Z.}~\bibnamefont{Zhai}},
  \bibinfo{author}{\bibfnamefont{Y.}~\bibnamefont{Wang}}, \bibnamefont{and}
  \bibinfo{author}{\bibfnamefont{H.}~\bibnamefont{Jiang}},
  \bibinfo{journal}{Proceedings of the National Academy of Sciences of the
  United States of America} \textbf{\bibinfo{volume}{115}},
  \bibinfo{pages}{2032} (\bibinfo{year}{2018}).

>>>>

\section{Results and discussion}
\subsection{BITSS method}
\begin{figure}[tb]
  \includegraphics[width=\linewidth]{toy2d.pdf}
  \caption{\label{fig:toy2d}
    (a) The trajectories of the two states under the BITSS method (orange line) for a simple 2D potential with two minima (blue dots).
        The transition state is shown by a red dot, and the minimum energy pathway by the dashed line.
    (b) A snapshot of the BITSS minimisation showing the driving forces on each state due to the energy constraint, $\bm{F}_E$, and distance constraint, $\bm{F}_D$, with $E_1 < E_2$ and $\mathrm{d}(\bm{x}_1,\bm{x}_2) < d_i$.
    (c) The final configuration of the BITSS method showing the two states in orange, the transition state in red, and the negative curvature eigenvector, $\bm{\hat{\tau}}$.
  }
\end{figure}

@@

\subsection{Speed Comparison}
\begin{figure*}[tb]
  \includegraphics[width=\linewidth]{speedtest.pdf}
  \caption{\label{fig:speedtest}
    Comparisons between BITSS, DNEB, and the string method in the convergence to the transition state as a function of the number of calculations of the energy gradient.
    Three test systems are used: (a) a Lennard-Jones seven-particle cluster, (b) cylindrical shell buckling, and (c) wetting of a chemically-striped surface.
    The configurations shown correspond to the two minimum energy states and the transition state, marked by an asterisk.
    The string method and DNEB are repeated with a differing number of images, as listed in the legend in (c).
  }
\end{figure*}

@@

\subsection{Adaptive discretisation}\label{sec:adaptive}
\begin{figure}[tb]
  \includegraphics[width=\linewidth]{adaptivemesh.pdf}
  \caption{\label{fig:adaptivemesh}
    (a) Snapshots of the BITSS method applied to the buckling of a cylinder with a changing mesh.
        The radial displacement relative the unbuckled cylinder is shown, as well as the underlying triangular mesh.
    (b) BITSS applied to the striped wetting example with different resolutions for the two states.
        Each grid cell denotes 50x50 lattice nodes.
        The zoomed axis shows the difference in the fluid interface between the two final states, as well as the approximated transition state (solid black line).
        This is compared to the transition state found using a high resolution (dashed line).
  }
\end{figure}

@@

\subsection{Complex landscapes}
\begin{figure}[tb]
  \includegraphics[width=\linewidth]{flatdiscontinuous.pdf}
  \caption{\label{fig:flatdiscontinuous}
    (a) Energy profile of the BITSS pathway on a 2D potential with flat regions.
        Blue and red dots denote the minima and transition state, respectively.
        Points of interest are labelled by i--iii (see text).
        Top inset: A zoomed in view around the transition state.
        Bottom inset: The pathway taken, with the edges of the flat regions marked by dashed lines.
    (b) Disconnectivity graph of the energy landscape for a seven-particle cluster with a discontinuous hard-core pair potential (orange), and a standard Lennard-Jones potnetial (gray).
        The two graphs are offset for visibility.
    (c) Plot of the discontinuous potential.
        The repulsive section of the standard Lennard-Jones potential is also shown in grey.
  }
\end{figure}

@@

%% start bib
% % \bibliography{../../library.bib}
% \bibliography{bibexport.bib}
% \bibliographystyle{naturemag}
%% mid bib
\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\providecommand{\bibinfo}[2]{#2}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{Bryngelson1995}
\bibinfo{author}{Bryngelson, J.~D.}, \bibinfo{author}{Onuchic, J.~N.},
  \bibinfo{author}{Socci, N.~D.} \& \bibinfo{author}{Wolynes, P.~G.}
\newblock \bibinfo{title}{{Funnels, pathways, and the energy landscape of
  protein folding: A synthesis}}.
\newblock \emph{\bibinfo{journal}{Proteins: Structure, Function, and
  Bioinformatics}} \textbf{\bibinfo{volume}{21}}, \bibinfo{pages}{167--195}
  (\bibinfo{year}{1995}).

\bibitem{Onuchic1997}
\bibinfo{author}{Onuchic, J.~N.}, \bibinfo{author}{Luthey-Schulten, Z.} \&
  \bibinfo{author}{Wolynes, P.~G.}
\newblock \bibinfo{title}{{Theory of Protein Folding: The Energy Landscape
  Perspective}}.
\newblock \emph{\bibinfo{journal}{Annual Review of Physical Chemistry}}
  \textbf{\bibinfo{volume}{48}}, \bibinfo{pages}{545--600}
  (\bibinfo{year}{1997}).

\bibitem{Boehr2006}
\bibinfo{author}{Boehr, D.~D.}, \bibinfo{author}{McElheny, D.},
  \bibinfo{author}{Dyson, H.~J.} \& \bibinfo{author}{Wrightt, P.~E.}
\newblock \bibinfo{title}{{The dynamic energy landscape of dihydrofolate
  reductase catalysis}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{313}},
  \bibinfo{pages}{1638--1642} (\bibinfo{year}{2006}).

\bibitem{Kerns2015}
\bibinfo{author}{Kerns, S.~J.} \emph{et~al.}
\newblock \bibinfo{title}{{The energy landscape of adenylate kinase during
  catalysis}}.
\newblock \emph{\bibinfo{journal}{Nature Structural and Molecular Biology}}
  \textbf{\bibinfo{volume}{22}}, \bibinfo{pages}{124--131}
  (\bibinfo{year}{2015}).

\bibitem{Guo2018a}
\bibinfo{author}{Guo, C.}, \bibinfo{author}{Wang, Z.}, \bibinfo{author}{Wang,
  D.}, \bibinfo{author}{Wang, H.~F.} \& \bibinfo{author}{Hu, P.}
\newblock \bibinfo{title}{{First-Principles Determination of CO Adsorption and
  Desorption on Pt(111) in the Free Energy Landscape}}.
\newblock \emph{\bibinfo{journal}{Journal of Physical Chemistry C}}
  \textbf{\bibinfo{volume}{122}}, \bibinfo{pages}{21478--21483}
  (\bibinfo{year}{2018}).

\bibitem{Richardson2016}
\bibinfo{author}{Richardson, J.~O.} \emph{et~al.}
\newblock \bibinfo{title}{{Concerted hydrogen-bond breaking by quantum
  tunneling in the water hexamer prism}}.
\newblock \emph{\bibinfo{journal}{Science}} \textbf{\bibinfo{volume}{351}},
  \bibinfo{pages}{1310} (\bibinfo{year}{2016}).

\bibitem{Vaillant2019}
\bibinfo{author}{Vaillant, C.~L.}, \bibinfo{author}{Althorpe, S.~C.} \&
  \bibinfo{author}{Wales, D.~J.}
\newblock \bibinfo{title}{{Path Integral Energy Landscapes for Water
  Clusters}}.
\newblock \emph{\bibinfo{journal}{Journal of Chemical Theory and Computation}}
  \textbf{\bibinfo{volume}{15}}, \bibinfo{pages}{33--42}
  (\bibinfo{year}{2019}).

\bibitem{Richard2018}
\bibinfo{author}{Richard, D.} \& \bibinfo{author}{Speck, T.}
\newblock \bibinfo{title}{{Crystallization of hard spheres revisited. I.
  Extracting kinetics and free energy landscape from forward flux sampling}}.
\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
  \textbf{\bibinfo{volume}{148}}, \bibinfo{pages}{124110}
  (\bibinfo{year}{2018}).

\bibitem{Wales1998}
\bibinfo{author}{Wales, D.~J.}, \bibinfo{author}{Miller, M.~A.} \&
  \bibinfo{author}{Walsh, T.~R.}
\newblock \bibinfo{title}{{Archetypal energy landscapes}}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{394}},
  \bibinfo{pages}{758--760} (\bibinfo{year}{1998}).

\bibitem{Wales2012}
\bibinfo{author}{Wales, D.~J.}
\newblock \bibinfo{title}{{Decoding the energy landscape: Extracting structure,
  dynamics and thermodynamics}}.
\newblock \emph{\bibinfo{journal}{Philosophical Transactions of the Royal
  Society A: Mathematical, Physical and Engineering Sciences}}
  \textbf{\bibinfo{volume}{370}}, \bibinfo{pages}{2877--2899}
  (\bibinfo{year}{2012}).

\bibitem{Panter2019}
\bibinfo{author}{Panter, J.~R.}, \bibinfo{author}{Chen, J.},
  \bibinfo{author}{Zhang, T.} \& \bibinfo{author}{Kusumaatmaja, H.}
\newblock \bibinfo{title}{{Harnessing energy landscape exploration to control
  the buckling of cylindrical shells}}.
\newblock \emph{\bibinfo{journal}{Communications Physics}}
  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{151} (\bibinfo{year}{2019}).

\bibitem{Hutchinson2018}
\bibinfo{author}{Hutchinson, J.~W.} \& \bibinfo{author}{Thompson, J. M.~T.}
\newblock \bibinfo{title}{{Imperfections and energy barriers in shell
  buckling}}.
\newblock \emph{\bibinfo{journal}{International Journal of Solids and
  Structures}} \textbf{\bibinfo{volume}{148-149}}, \bibinfo{pages}{157--168}
  (\bibinfo{year}{2018}).

\bibitem{Zhang2014}
\bibinfo{author}{Zhang, Y.} \& \bibinfo{author}{Ren, W.}
\newblock \bibinfo{title}{{Numerical study of the effects of surface topography
  and chemistry on the wetting transition using the string method}}.
\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
  \textbf{\bibinfo{volume}{141}}, \bibinfo{pages}{244705}
  (\bibinfo{year}{2014}).

\bibitem{Panter2019b}
\bibinfo{author}{Panter, J.~R.}, \bibinfo{author}{Gizaw, Y.} \&
  \bibinfo{author}{Kusumaatmaja, H.}
\newblock \bibinfo{title}{{Multifaceted design optimization for superomniphobic
  surfaces}}.
\newblock \emph{\bibinfo{journal}{Science Advances}}
  \textbf{\bibinfo{volume}{5}}, \bibinfo{pages}{eaav7328}
  (\bibinfo{year}{2019}).

\bibitem{Amabili2017}
\bibinfo{author}{Amabili, M.}, \bibinfo{author}{Giacomello, A.},
  \bibinfo{author}{Meloni, S.} \& \bibinfo{author}{Casciola, C.~M.}
\newblock \bibinfo{title}{{Collapse of superhydrophobicity on nanopillared
  surfaces}}.
\newblock \emph{\bibinfo{journal}{Physical Review Fluids}}
  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{034202} (\bibinfo{year}{2017}).

\bibitem{Othayoth2020}
\bibinfo{author}{Othayoth, R.}, \bibinfo{author}{Thoms, G.} \&
  \bibinfo{author}{Li, C.}
\newblock \bibinfo{title}{{An energy landscape approach to locomotor
  transitions in complex 3D terrain}}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences}} \textbf{\bibinfo{volume}{117}}, \bibinfo{pages}{14987--14995}
  (\bibinfo{year}{2020}).

\bibitem{Filipov2015}
\bibinfo{author}{Filipov, E.~T.}, \bibinfo{author}{Tachi, T.},
  \bibinfo{author}{Paulino, G.~H.} \& \bibinfo{author}{Weitz, D.~A.}
\newblock \bibinfo{title}{{Origami tubes assembled into stiff, yet
  reconfigurable structures and metamaterials}}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences of the United States of America}} \textbf{\bibinfo{volume}{112}},
  \bibinfo{pages}{12321} (\bibinfo{year}{2015}).

\bibitem{Zhai2018}
\bibinfo{author}{Zhai, Z.}, \bibinfo{author}{Wang, Y.} \&
  \bibinfo{author}{Jiang, H.}
\newblock \bibinfo{title}{{Origami-inspired, on-demand deployable and
  collapsible mechanical metamaterials with tunable stiffness}}.
\newblock \emph{\bibinfo{journal}{Proceedings of the National Academy of
  Sciences of the United States of America}} \textbf{\bibinfo{volume}{115}},
  \bibinfo{pages}{2032--2037} (\bibinfo{year}{2018}).

\bibitem{Bertoldi2017}
\bibinfo{author}{Bertoldi, K.}, \bibinfo{author}{Vitelli, V.},
  \bibinfo{author}{Christensen, J.} \& \bibinfo{author}{{Van Hecke}, M.}
\newblock \bibinfo{title}{{Flexible mechanical metamaterials}}.
\newblock \emph{\bibinfo{journal}{Nature Reviews Materials}}
  \textbf{\bibinfo{volume}{2}}, \bibinfo{pages}{17066} (\bibinfo{year}{2017}).

\bibitem{Truby2016}
\bibinfo{author}{Truby, R.~L.} \& \bibinfo{author}{Lewis, J.~A.}
\newblock \bibinfo{title}{{Printing soft matter in three dimensions}}.
\newblock \emph{\bibinfo{journal}{Nature}} \textbf{\bibinfo{volume}{540}},
  \bibinfo{pages}{371--378} (\bibinfo{year}{2016}).

\bibitem{Chi2022}
\bibinfo{author}{Chi, Y.} \emph{et~al.}
\newblock \bibinfo{title}{{Bistable and Multistable Actuators for Soft Robots:
  Structures, Materials, and Functionalities}}.
\newblock \emph{\bibinfo{journal}{Advanced Materials}}  (\bibinfo{year}{2022}).

\bibitem{Bonfanti2020}
\bibinfo{author}{Bonfanti, S.}, \bibinfo{author}{Guerra, R.},
  \bibinfo{author}{Font-Clos, F.}, \bibinfo{author}{Rayneau-Kirkhope, D.} \&
  \bibinfo{author}{Zapperi, S.}
\newblock \bibinfo{title}{{Automatic design of mechanical metamaterial
  actuators}}.
\newblock \emph{\bibinfo{journal}{Nature Communications}}
  \textbf{\bibinfo{volume}{11}}, \bibinfo{pages}{4162} (\bibinfo{year}{2020}).

\bibitem{Shan2015}
\bibinfo{author}{Shan, S.} \emph{et~al.}
\newblock \bibinfo{title}{{Multistable Architected Materials for Trapping
  Elastic Strain Energy}}.
\newblock \emph{\bibinfo{journal}{Advanced Materials}}
  \textbf{\bibinfo{volume}{27}}, \bibinfo{pages}{4296--4301}
  (\bibinfo{year}{2015}).

\bibitem{Giri2021}
\bibinfo{author}{Giri, T.~R.} \& \bibinfo{author}{Mailen, R.}
\newblock \bibinfo{title}{{Controlled snapping sequence and energy absorption
  in multistable mechanical metamaterial cylinders}}.
\newblock \emph{\bibinfo{journal}{International Journal of Mechanical
  Sciences}} \textbf{\bibinfo{volume}{204}}, \bibinfo{pages}{106541}
  (\bibinfo{year}{2021}).

\bibitem{Cerjan1981}
\bibinfo{author}{Cerjan, C.~J.} \& \bibinfo{author}{Miller, W.~H.}
\newblock \bibinfo{title}{{On finding transition states}}.
\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
  \textbf{\bibinfo{volume}{75}}, \bibinfo{pages}{2800--2806}
  (\bibinfo{year}{1981}).

\bibitem{Heyden2005}
\bibinfo{author}{Heyden, A.}, \bibinfo{author}{Bell, A.~T.} \&
  \bibinfo{author}{Keil, F.~J.}
\newblock \bibinfo{title}{{Efficient methods for finding transition states in
  chemical reactions: Comparison of improved dimer method and partitioned
  rational function optimization method}}.
\newblock \emph{\bibinfo{journal}{Journal of Chemical Physics}}
  \textbf{\bibinfo{volume}{123}}, \bibinfo{pages}{224101}
  (\bibinfo{year}{2005}).

\bibitem{Kastner2008}
\bibinfo{author}{K{\"{a}}stner, J.} \& \bibinfo{author}{Sherwood, P.}
\newblock \bibinfo{title}{{Superlinearly converging dimer method for transition
  state search}}.
\newblock \emph{\bibinfo{journal}{Journal of Chemical Physics}}
  \textbf{\bibinfo{volume}{128}}, \bibinfo{pages}{014106}
  (\bibinfo{year}{2008}).

\bibitem{Zhang2016}
\bibinfo{author}{Zhang, L.}, \bibinfo{author}{Du, Q.} \&
  \bibinfo{author}{Zheng, Z.}
\newblock \bibinfo{title}{{Optimization-based Shrinking Dimer Method for
  Finding Transition States}}.
\newblock \emph{\bibinfo{journal}{SIAM Journal on Scientific Computing}}
  \textbf{\bibinfo{volume}{38}}, \bibinfo{pages}{A528--A544}
  (\bibinfo{year}{2016}).

\bibitem{E2007}
\bibinfo{author}{E, W.}, \bibinfo{author}{Ren, W.} \&
  \bibinfo{author}{Vanden-Eijnden, E.}
\newblock \bibinfo{title}{{Simplified and improved string method for computing
  the minimum energy paths in barrier-crossing events}}.
\newblock \emph{\bibinfo{journal}{The Journal of Chemical Physics}}
  \textbf{\bibinfo{volume}{126}}, \bibinfo{pages}{164103}
  (\bibinfo{year}{2007}).

\bibitem{Ren2013}
\bibinfo{author}{Ren, W.} \& \bibinfo{author}{Vanden-Eijnden, E.}
\newblock \bibinfo{title}{{A climbing string method for saddle point search}}.
\newblock \emph{\bibinfo{journal}{Journal of Chemical Physics}}
  \textbf{\bibinfo{volume}{138}}, \bibinfo{pages}{134105}
  (\bibinfo{year}{2013}).

\bibitem{E2002}
\bibinfo{author}{E, W.}, \bibinfo{author}{Ren, W.} \&
  \bibinfo{author}{Vanden-Eijnden, E.}
\newblock \bibinfo{title}{{String method for the study of rare events}}.
\newblock \emph{\bibinfo{journal}{Physical Review B}}
  \textbf{\bibinfo{volume}{66}}, \bibinfo{pages}{052301}
  (\bibinfo{year}{2002}).
